Constructing the transition graphs of interacting hysterons

### 2022-05-25 Paper_draft.tex
Added figure for N=2 and N=3 base graphs

@@

Scrambling entails that the ordering of switching fields can change throughout the graph. In order to discuss scrambling more explicitly, we here define the concept of the main loop of a transition graph. We define the up and down boundaries of the main loop as the series of up transitions going from the all-zero to the all-one state, and the series of down transitions going from the all-one to the all-zero state, respectively. In general, we account for exchange symmetry by fixing the ordering of the up boundary. Therefore, we often refer to the down boundary of the main loop as simply the main loop.\\
In the Preisach model, the ordering of the main loop fixes the transitions throughout the transition graph, so that each main loop corresponds to a unique Preisach graph. Because the down boundary of the main loop has $N!$ permutations, there are $N!$ Preisach graphs for a system of $N$ hysterons.\\

>>>>

    \includegraphics[width=0.5\textwidth]{base_graphs.png}
    \caption{All possible base graphs for the two- and three-hysteron systems. a) All base graphs for $N=2$; since scrambling is not possible for $N=2$, the base graphs are the two Preisach graphs. b) Preisach graphs for $N=3$. c) Scrambled base graphs for N=3 that are possible for linear coupling.}
    \label{fig:basegraphs_n3}

@@

Scrambling entails that the ordering of switching fields can change throughout the graph. In order to discuss scrambling more explicitly, we here define the main loop as the series of up and down transitions connecting the two saturated states. In the Preisach model, the ordering of the main loop fixes the transitions throughout the transition graph, so that each main loop corresponds to a unique Preisach graph. Because the down boundary of the main loop has $N!$ permutations, there are $N!$ Preisach graphs for a system of $N$ hysterons.\\
